\paragraph{Sphere packing problem}
What is the largest fraction of $ℝ^d$ that can be covered by a collection of congruent balls with disjoint interiors?
sphere packing $\P⊂ℝ^d$. THe upper density is
\[\limsup_{r→∞}\f{|B_r^d(0)∩\P|}{|B_r^d(0)|}\]
sphere packing density $Δ_{ℝ^d}$ is the sup over all upper densities.

Groemer: there exists an optimal sphere packing. Find it!

$d=1$ $\checkmark$

$d=2$: Thue (1910) Hexagonal lattice: put balls in the cenetrs of the hexagons that touch the hexagons from the inside. This is the best possible.
\[Δ_{ℝ^2}=\fπ{2\sqrt 3}\approx 0.09…\]
(square lattice is worse, $\fπ4\approx 0.79…$.)

$d=3$ Kepler's problem. Hales (2005), Hales et al.\ (2015): Face-centered cubic packing is the best possible.

$d=8$ M.\ Viasovska (2016)

$d=24$

Why $d=8$ special?

Lower bounds: $Δ_{ℝ^d}\geq2^{-d}$. Covering argument

\paragraph{Lattices and periodic packings} Lattice in $ℝ^d$ is the image of $ℤ^d$ under invariant linear transformation. Sphere packing $\P$ is periodic if there exists a lattice $Λ$ such that $\P$ is invariant under translation by every element of $Λ$. A lattice packing is a periodic packing in which the spheres form a single orbit under the translation symmetry group. 

lattice packings $⊂$ periodic packings, and those come arbitrarily close to $Δ_{ℝ^d}$.

Let $Λ$ be a lattice with basis $v_1,…,v_d$ fundamental cell of $Λ$ with respect to this basis
\[C=\{x_1v_1+…+x_dv_d:0\leq x_1<1,\ 1\leq i\leq d\}\]
Take balls $B_r^d$ where $r=\f12$ length of shortest nonzero vector in $Λ$. The density of $Λ$ then is
\[\f{|B_r^d|}{|C|}=\f{\f{π^{\f d2}}{(\f d2!}r^d}{|\det(v_1,…,v_d)|}\]
where the denominator is $\vol(\f{ℝ^d}Λ)$
The density of a periodic packing is
\[\f{N|B_r^d|}{\vol(\f{ℝ^d}Λ)}\]

$E_8$ lattice ($⊂ℝ^8$) $v_1,v_2,…,v_8∈ℝ^8$. Dynkin diagram (linking consecutive numbers and 3 and 5)

For $i\neq j$
\[\langle v_i,v_j\rangle =
	\begin{cases}
		-1 &\tx{if nodes $i,j$ are linked by an edge}\\
		0
	\end{cases}
\]
$\|v_i\|^2=2$. $G=(\langle v_i,v_j\rangle)_{i,j=1}^8$. $\det(G-tI)\approx t^8-t^7+t^6-t^5+t^4-t^3+t^2-t^1$ has no roots when $t<0$ because every term is the positive. Why is $E_8$ so special? It is integral (all inner products between vectors in $E_8$ are integers), integral (squared length of every vector is an even integer
\[|\sum_{j=1}^8m_jv_j|^2=2\sum_{j=1}^8m_j^2+\sum_{i\neq j}2m_im_j\langle v_i,v_j\rangle\] only distances $(\sqrt{2k})_{k=1,2,3,…}$ appear as distances in the lattice),
unimodular ($\def(G)=1=\vol(\f{ℝ^d}Λ)^2$), self dual ($E_8=E_8^*$), where
\[Λ^*=\{y∈ℝ^d:\langle x,y\rangle∈ℤ,\ ∀x∈Λ\}\], $v_1,…,v_d$ basis of $Λ$, $v_j^*(v_i)=δ_{ij}$.

\begin{lem} 
	If $Λ$ is integral and unimodular then $Λ$ is self dual.
\end{lem}
\begin{proof}
	$Λ$ integral $⇔Λ⊂Λ^*$. $Λ$ is unimodular
	\[[Λ^*:Λ]=\f{\vol(\f{ℝ^d}Λ)}{\vol(\f{ℝ^d}Λ)}=\vol(\f{ℝ^d}Λ)^2=1\]
	and is the unique such lattice in $ℝ^8$!
\end{proof}

Fourier analysis: Cohn-Elkies (2003): Linear programming bounds
\[\wh f(y)=∫_{ℝ^d}f(x)e^{-2πixy}\md x\]
$f,\wh f∈L^1(ℝ^d)$ then
\[f(x)=∫_{ℝ^d}\wh f(y)e^{2πixy}\md y\]
\[\wh{τ_tf}=e^{2πit\cdot}\wh f\]
Poisson summation:
\[(Pf)(x)=\sum_{m∈ℤ^d}f(x+m)∈L^1(Π=[-\f12,\f12]^d)\]
\[\|Pf\|_{L^1(Π^d)}\leq\|fu|_{L^1(ℝ^d)}\]
\[\wh{Pf}(k)=\sum_m∫_{[-\f12,\f12]^d}f(x+m)e^{-2πik}\md x=\sum_m∫_{m+[-\f12,\f12]^d}\ub{e^{2πikm}_1\md y=\wh f(k)\]
	\[(Pf)(x)=\sum_{k∈ℤ^d}\wh{Pf}(k)e^{2πikx}\]
	\[\sum_{m∈ℤ^d}f(x+m)=\sum_{k∈ℤ^d}\wh f(k)e^{2πikx}\]
	at $x=0$
	\[\sum_{m∈ℤ^d}f(m)=\sumv{k∈ℤ^d}\wh f(k)\]
	In a lattice $Λ$,
	\[\sumv{x∈Λ}f(x)=\f1{\vol(\f{ℝ^d}Λ)}\sum_{y∈Λ^*}\wh f(y)\]
	because
	\[\sum_{x∈Λ}f(x+t)=\f1{\vol(\f{ℝ^d}Λ)}\sum_{y∈Λ^*}\wh f(y)e^{2πiyt}\]
	\begin{theo} Let $r>9$ and $f:ℝ^d→ℝ$ Schwartz such that $f(0)=\wh f(0)>0,\ \wh f(y)\geq 0\ (∀y∈ℝ^d),\ f(x)\leq 0,\ (∀|x|\geq r)$. Then \[∇_{ℝ^d}\leq\vol(B_{\f r2}^d)\]
	\end{theo}
	\begin{proof} Step 1: Lattice packings. $Λ⊂ℝ^d$ lattice. Then its density is $\f{\vol(B_{\f r2}^d)}{\vol(\f{ℝ^d}Λ)}$ with $r$ minimal length in $Λ$. Wts $\vol(\f{ℝ^d}Λ)\geq 1$. Poisson implies
		\[f(0)\geq\sum_{x∈Λ}f(x)=\f1{\vol(\f{ℝ^d}Λ)}\sum_{y∈Λ^*}\wh f(y)\geq\f{\wh f(0)}{\vol(\f{ℝ^d}Λ)},\] done.

		Step 2: periodic packings. Density $\f{N\vol(\f{ℝ^d}Λ)}{\vol(\f{ℝ^d}Λ)}$, wts $\vol(\f{ℝ^d}Λ)\geq N$: Poisson implies
		\[Nf(0)\sum_{j,k=1}^N\sum_{x∈Λ}f(t_j-t_k+)=\f1{\vol(\f{ℝ^d}Λ)}\sum_{y∈Λ^*}\wh f(y)|\sum_{j=1}^Ne^{2πiyt_j}|^2\geq\f{N^2\wh f(0)}{\vol(\f{ℝ^d}Λ)}\]
		Step 3: Approximate.
	\end{proof}
	\begin{itemize}
		\item Equality iff $f$ vanishes of $Λ\setminus 0$ and $\wh f$ vanishes on $Λ^*\setminus 0$.
		\item wlog $f,\wh f$ are radially symmetric.
		\item $f=\f{f+\wh f}2+\f{f-\wh f}2=:f_++f_-$. Then $\wh f_+=f_+$ and $\wh f_-=-f_-$.
	\end{itemize}
	Goel: Construct radial (Schwartz) eigenfunctions of the Fourier transform with prescribed roots (at $\sqrt 2,\sqrt 4,\sqrt 6,\sqrt8,…$). "The sphere packing problem in dimension 8" Annals of Math (2016)

	$f(x)=e^{-π|x|^2}$ satisfies $f=\wh f$.
	\[f()=∫_0^∞e^{-π|x|^2t}g(t)\md t\]
	\[\wh f(y)>∫_{ℝ^d}∫_0^∞e^{-π|x|^2tg(t)\md te^{-2πixy}\md x=∫_0^∞g(t)t^{-\f d2}e^{-\f{π|y|^2}t}\md t=∫_0^∞g(\f1t)t^{\f d2}e^{-π|y|^2t}\f{\md t}{t^2}\]
		if 
		\[g(t)=t^{\f d2-2}g(\f1t)\] + Analytic number theory… (modular forms: Theta series, Eisenstein "series" …)
