Recall, that a Kakeya set is a compact set $E⊂ℝ^d$ which contains a unit line segment in every possible direction. We have seen, that if $d\geq 2$, then there are Kakeya sets in $ℝ^d$ of zero (Lebesque) measure. The Kakeya (set) conjecture is: If $E⊂ℝ^d$ is a Kakeya set, then $E$ has Hausdorff dimension $d$. We have seen it for $d=2$, but remains an open problem in general $d$. However
\[\dim E\geq\max\{\f{d+2}2,(2-\sqrt 2)(d-4)+3\}\]
is already shown, where the first constant is due to Wolff '95 and the second due to Katz-Tao '02.

\paragraph{Kakeya maximal function} Let $δ>0,\ e∈\se^{d-1},\ a∈ℝ^d$. Let $T_e^δ(a)$ be the cylinder centered at $a$, base diameter $δ$, oriented along $e$ with length $2|e|$. Let $f∈L^1_\loc(ℝ^d)$. Then we define
\[f_δ^*(e)=\sup_{a∈ℝ^d}\f1{|T^δ|}∫_{T_e^δ(a)}|f|\]
Note, that $|T_e^δ(a)|$ only depends on $δ$.
\begin{rem}
	\begin{enumerate}
		\item trivially \[\|f^*_δ\|_{L^∞(\se^{d-1})}\leq\|f\|_{L^∞(ℝ^d)},\]
			\[\|f^*_δ\|_{L^∞(\se^{d-1})}\leqδ^{-(d-1)}\|f\|_{L^1(ℝ^d)}\]
		\item If $d\geq 2$ and $p<∞$ then there are no bounds of the form
			\[\|f^*_δ\|_{L^q(\se^{d-1})}\leq c\|f\|_{L^p(ℝ^d)}\]
			with $c$ independent of $δ$. Why: Let $E$ be a Kakeya set with zero measure and $E_δ$ a $δ$ neighborhood of $E$, $f=1_{E_δ}$. Then
			\begin{itemize}
				\item $∀e∈\se^{d-1}\ f^*_δ(e)=1\therefore\|f^*_δ\|_{L^q(\se^{d-1})}\sim 1$
				\item $\|f\|_{L^p}=|E_δ|^{\f1p}$ which goes to $0$ as $δ→0^+$ if $p<∞$.
			\end{itemize}
			Goal: $δ^{-ε}$ estimate for $f_δ^*$, i.e.\ $∀ε>0\ ∃C_ε<∞$
			\[\|f^*_δ\|_{L^p(\se^{d-1})}\leq C_εδ^{-ε}\|f\|_{L^p(ℝ^d)}\] for some $p<∞$. 
		\item This inequality fails if $p<d$: $∀e∈\se^{d-1}:B(0,δ)⊂T_e^δ(0)$. Let $f=1_{B(0,δ)}$. Then
			\[f^*_δ(e)\geq\f{|B(δ)|}{|T^δ|}\sim\f{δ^d}{δ^{d-1}}=δ\implies\|f^*_δ\|_{L^p(\se^{d-1})}\gtrsim δ\]
			\[\|f\|_{L^p}=|B(δ)|^{\f1p}=δ^{\f dp}\]
			So we must have $p\geq d$ for the inequality to hold for all $δ$. Kakeya maximal function conjecture: It holds for $p=d$. 
			\begin{itemize}
				\item $d=2$: Cordoba '77, Bourgain '91 (seen: $R_δ^*$, $\|f^*_δ\|_{L^2(\se^1)}\lesssim\sqrt{\log\f1δ}\|f\|_{L^2(ℝ^2)}$)
				\item $d\geq 3$ open,…
				\item If the inequality holds for some finite $p<∞$, then Kakeya sets in $ℝ^d$ have Hausdorff dimension $d$.
			\end{itemize}
	\end{enumerate}
\end{rem}
\paragraph{Restriction conjecture (on $\se^{d-1},σ$)}
\[\|\wh{fσ}\|_{L^p(ℝ^d)}\lesssim_{p,d}\|f\|_{L^∞(\se^{d-1})}\]
if $p>\f{2d}{d-1}$. This is equivalent to
\[\|\wh{fσ}\|_{L^p(ℝ^d)}\lesssim\|f\|_{L^p(\se^{d-1})}\]
if $p>\f{2d}{d-1}$, which is due to Bourgain.

Upshot: The restriction conjecture implies the Kakeya maximal function conjecture and hence the Kakeya set conjecture. (Unknown if these two are equivalent)

\begin{theo} If the inequality is true, then the conjectured bound
	\[\|f^*_δ\|_{L^d(\se^{d-1})}\lesssim_εδ^{-ε}\|f\|_{L^d(ℝ^d)}\]
	is also true.
\end{theo}
\begin{lem}[Duality]
	Let $1<p<∞,\ p'=\f p{p-1}$, $\{e_k\}⊂\se^{d-1}$. Assume, that if $\{e_k\}$ is maximal $δ$-separated set and $δ^{d-1}\sum_ky_k^{p'}\leq 1$, then
	\[\|\sum_ky_k1_{T_{e_k}^δ(a_k)}\|_{L^{p'}(ℝ^d)}\leq A.\]
	Then there is a bound 
	\[\|f^*_δ\|_{L^p(\se^{d-1})}\lesssim A\|f\|_{L^p(ℝ^d)}\]
\end{lem}
(why is it called 'Duality Lemma'?)
\begin{proof}[Proof of lemma]
	$|e-e'|<δ⇒f^*_δ(e)\lesssim_d f^*_δ(e')$ because any $T_e^δ(a)$ can be covered by finitely many tubes $T_{e'}^δ(a')$. Therefore
	\[\|f^*_δ\|_{L^p(\se^{d-1})}\leq(\sum_k∫_{D(e_k,δ)}|F^*_δ(e)|^p\mdσ_e)^{\f1p}\lesssim(δ^{d-1}\sum_k|f^*_δ(e_k)|^p)^{\f1p}=δ^{d-1}\sum_ky_k|f^*_δ(e_k)|\]
	for some sequence $(y_k)$ such that $\sum_ky_k^{p'}δ^{d-1}=1$, by duality of $l^p-l^{p'}$. Therefore
	\[\|f^*_δ\|_{L^p(\se^{d-1})}\lesssimδ^{d-1}\sum_k y_k\f1{|T^δ|}∫_{T_{e_k}^δ(a_k)}|f|\]
	for some choice of $(a_k)$ that realizes the sup. This equals
	\[∫_{ℝ^d}(\sum_ky_k1_{T_{e_k}^δ(a_k)})|f|\leq\|\sum_k y_k1_{T_{e_k}^δ(a_k)}\|_{L^{p'}(ℝ^d)}\|f\|_{L^p(ℝ^d)}\lesssim A\|f\|_{L^p(ℝ^d)}\]
\end{proof}
\begin{proof}[Proof of theorem]
	Choose maximal $δ$-seperated set $\{e_j\}⊂\se^{d-1}$ (of cardinality $\simδ^{-(d-1)}$). Take a cap of size $δ$. Encapsulate it by a cylinder $C_{j,δ}$ of size $δ,δ^2$ and let $c_j=\se^{d-1}∩C_{j,δ}$. Recall Knapp: functions $f_j∈L^∞(\se^{d-1}):\supp(f_j)⊂c_j$ such that $\|f_j\|_{L^∞(\se^{d-1})}=1$ and
	\[|\wh{f_jσ}(x)|\gtrsim|c_j|\simδ^{d-1}\]
	if $x∈τ_j$. Idea: take functions of the form
	\[f_ω=\sum_jω_jy_jf_j\]
	where $y_j\geq 0,\ ω_j\pm 1$ iid.

	Khinchine's inequality:
	$(ω_n)_{n=1}^N$ iid variables taking values $\pm1$ with equal probability. Then
	\[\E(|\sum_{n=1}^Na_nω_n|^p)^{\f1p}\simeq_p(\sum_{n=1}^N|a_n|^2)^{\f12}\]
	where $(a_n)⊂ℂ$.
	(We now write $q$ instead of $p$)
	\[\|f_ω\|_{L^q(\se^{d-1})}^q=\sum_j\|y_jf_j\|_{L^q(\se^{d-1})}^q=a\sum_jy_j^q|c_j|\sim\sum_jy_j^qδ^{d-1}\]
	\[\E_ω(\|\wh{f_ωσ}\|_{L^q(ℝ^d)}^q)=∫_{ℝ^d}E_ω(|\wh{f_ωσ}(x)|^q)\md x\simeq∫_{ℝ^d}(\sum y_j^2|\wh{f_jσ}(x)|^2)^{\f q2}\md x\gtrsimδ^{q(d-1)}∫_{ℝ^d}|\sum_jy_j^21_{τ_j}(x)|^{\f q2}\md x\]
	By the restriction inequality the first term is up to a constant bounded by 
	\[\sum y_j^qδ^{d-1}\] for every $q>\f{2d}{d-1}$. Now we rewrite. Set $ξ_j=y_j^2, p'=\f q2$. Then it is equivalent to
	\[\|\sum_jξ_j1_{τ_j}\|_{L^{\f q2}(ℝ^d)}\lesssimδ^{-2(d-1)}\]
	provided
	\[\sum_jξ_j^{p'}δ^{d-1}\leq 1\]
	for all $p'>\f d{d-1}$. Now dilate by $δ^2$
	\[\|\sumξ_j1_{T_j}\|_{L^{p'}(ℝ^d)}\lesssimδ^{2(\f d{p'}-(d-1))}\]
	if $\sum_jξ_j^{p'}δ^{d-1}\leq 1$ for all $p'>\f d{d-1}$. As $p'\downarrow\f d{d-1},\ \f d{p'}-(d-1)\uparrow 0$. Therefore
	\[∀ε>0\quad\|\sum ξ_j1_{T_j}\|_{L^{p'}(ℝ^d)}\lesssim_εδ^{-ε}\]
	if $δ^{d-1}\sumξ_j^{p'}\leq 1$ provided $p'$ is close enough to $\f d{d-1}$. Now by the duality lemma
	\[∀ε>0\quad\|f^*_δ\|_{L^p(\se^{d-1})}\lesssim_εδ^{-ε}\|f\|_{L^p(ℝ^d)},\]
	provided $p(<d)$ is close enough to $d$. Now interpolate with trivial $\|f^*_δ\|_{L^∞}\lesssim\|f\|_{L^∞}$ to finish the argument.
\end{proof}
