R.\ Gardener Bulletin AMS more about Brunn-Minkowski, geometrically, including more proofs, e.g.\ with induction of the dimension.

\paragraph{Hausdorff measure}
$E⊂ℝ^d$ any subset.
\[m_α^*(E):=\lim_{δ→0^+}\underbrace{\inf\{\sum_k(\diam F_k)^α:E⊂\bigcup_{k=1}^∞F_k\ \diam(F_k)\leqΔ\}}_{H_α^δ(E)}\]
exterior/outer $α$-dim Hausdorff measure. 
\begin{rem} $H_α^δ(E)\leq H_α^δ(E)\leq m_α^*(E)(∀δ>0)$. $H_α^δ(E)$ increases when $δ$ ecreases. $\therefore m_α^*(E)=\lim_{δ→0^+}H_α^δ(E)$ exists
\end{rem}

\begin{rem} Coverings must be by sets of arb. small measure. (If we allowed the $δ$ to be arbitrary then two parallel lines would get the same 1d-measure as one of them.)
\end{rem}
\begin{rem}[Scaling]
	"The measure of a set should scale like its dimension". E.g.: $Γ⊂ℝ^d$ smoot cureve of length $L$ $sim$ $λΓ$ has length $λL$. $Q⊂ℝ^d$ cube $sum$ $λQ$ has measure $λ^d|Q|$. $|F|$ scaled by $λ⇒(\diam F)^α$ scaled by $λ^α$
\end{rem}
\paragraph{Properties}
\begin{enumerate}
	\item $E_1⊂E_2⇒m_α^*(E_1)\leq m_α^*(E_2)$
	\item $\{E_j\}⊂ℝ^d$ countable family of sets $⇒m_α^*(\bigcup_{j=1}^∞E_j)\leq\sum_{j=1}^∞m_α^*(E_j)$
	\item (Finite additility) $\inf_{x∈E_1,y∈E_1}|x-y|=\dist(E_1,E_2)>0⇒m_α^*(E_1∪E_2)=m_α^*(E_1)+m_α^*(E_2)$
		\begin{proof} ETS $\geq$. Fix $0<ε<\dist(E_1,E_2)$. Given any cover of $E_1∪E_2$ with sets $F_1,F_,…$ of $\diam\leqδ<ε$, let $F_j'=F_j∩E_1,\ F_j''=F_j∩E_2$.
			\[\sum(\diam_j F_j')^α+\sum_j(\diam F_j'')^α\leq\sum_k\diam(F_k)^α\]
			Take inf over all covers, let $δ→0^+$, done.
		\end{proof}
		$m_α^*$ satisfies all properties of a Caratheodory outer measure $\therefore m_α^*$ is a countabley additive measure when restricted to Borel sets, call it $m_α$, the $α$-dim Hausdorff measure.
	\item $\{E_j\}$ countable family of disjoint Borel sets $⇒$
		\[m_α(\mathop{\dot\bigcup}_{j=1}^∞E_j)=\sum_{j=1}^∞m_α(E_j)\]
	\item Hausdorff masure is invariant under translation and rotations. It scales like:
		\[m_α(λE)=λ^αm_α(E)\]
	\item $m_0(E)=\#E,\ m_1(E)=|E|$ (=1D Lebesgue measure of $E$), $E⊂ℝ$ Borel.
	\item $E⊂ℝ^d$ Borel, $m_α(E)\simeq|E|$
		\begin{proof}
			\begin{enumerate}
				\item Isodiametric inequality: $|E|\leq v_d(\frac{\diam E}2)^d$, $v_d$ volume of the unit ball in $ℝ^d$. Prove first for sets $E=-E$ and then something hard.
				\item Covering argument: Given $ε,δ>0$, there exists a covering of $E$ by balls $\{B_j\}$: $\diam B_j<δ,\ \sum_j|B_j|\leq|E|+ε$
					\[H_d^δ(E)\leq\sum_j(\diam B_j)^d=c_d\sum_j|B_j|\leq c_d(|E|+ε),\]
					let $δ,ε→0^+$, get one of the inequalities.
			\end{enumerate}
		\end{proof}
	\item if $m_α^*(E)<∞$ and $β>α$, then $m_β^*(E)=0$. If $m_α^*(E)>0$ and $β<α$, then $m_β^(E)=∞$.
		\begin{proof}
			$\diam F<δ,β>α⇒(\diam F)^β=(\diam F)^{β-α}(\diam F)^α<δ^{β-α}(\diam F)^α$
		\end{proof}
		Consequence: Given $E⊂ℝ^d$ Borel, $∃!α$ such that
		\[m_β(E)=
			\begin{cases}
				∞&β<α\\0&β>α
			\end{cases}
		\]
		\[α=\sup\{β:m_β(E)=∞\}=\inf\{β:m_β(E)=0\}:=\text{Hausdorff dimension of $E$}=\dim E\]
		At the critical value $α=\dim E\ 0\leq m_α(E)\leq∞$. If $E$ is bounded and the inequalities are strict, we say that $E$ has strict Hausdorff dimension $α$.
\end{enumerate}
\begin{theo} The Cantor set $C⊂[0,1)$ has strict Hausdorff dimension $\frac{\log 2}{\log 3}$.
\end{theo}
ETS: $0<m_α(C)\leq 1$
\begin{proof} \highl{$m_α(C)\leq 1$:}
	$C=\bigcap C_k$ where each $C_k$ is a finite unionof $2^k$ inetrvals of length $3^{-k}$.. Given $δ>0$ coose $k$ large enough such that $3^{-k}<δ$. $C_k$ covers $C$ and Consists of $2^k$ intervals of diameter $3^{-k}<δ$. $H_α^δ(C)\leq 2^k(3^{-k})^α=1$, let $δ→0^+$, done.

	\highl{$m_α(C)>0$}:
	\begin{lem}%1
		$E\Subset d$ compact, $f:E→ℝ$ $γ$-Hölder, \[|f(x)-f(y)|\leq m|x-y|^γ\quad(∀x,y∈E)\quad 0<γ\leq 1\]
		Then
		\begin{enumerate}
			\item $m_β(f(E))\leq M^βm_α(E)$ if $β=\fracαγ$.\label{it:hölderhm}
			\item $\dim f(E)\leq\frac1γ\dim(E)$\label{it:hölderhd}
		\end{enumerate}
	\end{lem}
	\begin{proof} $\{F_k\}$ countable family of sets that covers $E$ $\therefore\{f(F_k∩E)\}$ covers $f(E)$. $\diam f(F_k∩E)\leq M(\diam F_k)^γ$.
		\[\sum_k(\diam f(EℵF_k))^{\fracαγ}\leq M^{\fracαγ}\sum_k(\diam F_k)^α,\] done. And \ref{it:hölderhm} implies \ref{it:hölderhd}.
	\end{proof}
	\begin{lem} The Cantor-Lebesgue function $F:C→[0,1]$ is $γ=\frac{\log 2}{\log 3}$-Hölder.
	\end{lem}%2
	\begin{proof}
		Goal: $|F(x)-F(y)|\leq c|x-y|^γ\ ∀x,y∈C$.

		$F_n$ increases at most $2^{-n}$ on an interval of length $3^{-n}$. $\therefore$ slope $\leq(\frac32)^n$ $\therefore |F_n(x)-F_n(y)|\leq(\frac32)^n|x-y|$. $|F_n(x)-F(x)|\leq2^{-n}$.
		Given $x,y$ chose $n$: $3^n|x-y|\sim1,\ 3^γ=2$.
		\begin{align*}
			|F(x)-F(y)|&\leq|F_n(x)-F_n(y)|+|F_n(x)-F(x)|+|F_n(y)-F(y)|\\
			    &\leq(\frac32)^n|x-y|+2\cdot 2^{-n}\leq c2^{-n}=c(3^{-n})^γ\leq c'|x-y|^γ
		\end{align*}
	\end{proof}
	Apply first lemma with $E=C,\ f=F,\ γ=\frac{\log 2}{\log 3}⇒1=m_1([0,1])\leq Mm_α(C)$, $\dim C=\frac{\log 2}{\log 3}$
\end{proof}

\paragraph{Rectifiable curves}
\begin{theo} $γ:[a,b]→ℝ^d$ continuous and simple. Then $γ$ is rectifiable iff $Γ=\{γ(t):a\leq t\leq b\}$ has strict Hausdorff dimension equal to 1. In that case $m_1(Γ)=l(γ)$.
\end{theo}
\begin{proof} $⇒$: Let $γ$ be rectifiable of length $L$. Consider arclength parametrization $\tildeγ$. $Γ=\{\tildeγ(s):0\leq s\le L\}$. \[|\tildeγ(s_1)-\tildeγ(s_2)|\leq|s_1-s_2|\]
	By first lemma \ref{it:hölderhm} $m_1(Γ)\leq L$. Why $m_1(Γ)\geq L$?
	\[Γ_j=\{γ(t):t_j\leq t\leq t_{j+1}\}\]
	\[Γ=\bigcup_{j=1}^{N-1}Γ_j\quad m_1(Γ)=\sum_{j=0}^{N-1}m_1(Γ_j)\]
	Claim: $m_1(Γ_j)\geq l_j:=|γ(t_j)-γ(t_{j+1})|$
	\begin{proof} $π:ℝ^2→ℝ,\ (x,y)↦x$ Lipschitz, $π(Γ_j)⊂[0,l_j]$ first lemma \ref{it:hölderhm} implies the claim.
	\end{proof}
	$\therefore m_1(Γ)\geq\sum m_1(Γ_j)\geq\sum l_j,\ L:=\sup_p\sum l_j\therefore m_1(Γ)\geq L$, done.

	(What about the other direction?)
\end{proof}
